\documentclass{beamer}
\usepackage{lmodern}
\mode<presentation> 
\usepackage{graphicx} % Required for inserting images
\usetheme{Berkeley}

%Information to be included in the title page:
\title{Quantum Computing Since Democritus: Scott Aaronson}
\author{Chapter 1 Summary: Atoms and the Void}
\institute{Saumya Chaturvedi}
% \date{2022}

\begin{document}

\begin{frame}
    \titlepage 
\end{frame}

\begin{frame}{Outline}
    \tableofcontents
\end{frame}

\section{Introduction: From Atoms}
\section{Introduction: Touchstone}
\section{Quantum Mechanics}
\section{Dilemma}
\section{The Different Interpretation Religions}
\section{Importance of Philosophy}
\section{Aha! Connection}

\begin{frame}
\frametitle{Introduction: From Atoms}
\begin{enumerate}

   \item Democritus in 400 BC
   \item Color and taste are not intrinsic to atoms
    % \pause 

\end{enumerate}

\end{frame}

\begin{frame}{Introduction: Touchstone}
    \begin{quote}
    Intellect: By convention there is sweetness, by convention bitterness, by convention color, in reality only atoms and the void.
    

    Senses: Foolish intellect! Do you seek to overthrow us, while it is from us that you take your evidence?
\end{quote}
\end{frame}


\begin{frame}
\frametitle{Quantum Mechanics}


\begin{itemize}

 \item RULE 1: it describes the evolution in time of the state of a region
 \item \alert{superposition} of all the possible configurations
of elementary particles in that region
 \item splitting into copies of ourselves
 \item RULE 2: act of measurement forces particle to choose 1 outcome probabilistically
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Dilemma}

\begin{enumerate}
 \item What IS a measurement?
\item Aren't physical laws supposed to be universal?
\item Modern Democritus Dilemma
\item Where do I put myself on the \alert{coherent superposition line}?
\end{enumerate}
\end{frame}
\begin{frame}
\frametitle{The Different Interpretation Religions}

\begin{enumerate}
    \item<1-> TYPE 1: There is no issue.
    \begin{itemize}
        \item Line between quantum experiment and measuring device
        \item Because a quantum state is just a representation of your knowledge
        \item Ex: Copenhagen and its Bayesian and Epistemic grandchildren
    \end{itemize}

    \item<2-> TYPE 2: What if I'm part of the quantum universe?
    \begin{itemize}
        \item Put yourself in coherent superposition
        \item Bohr's reply
        \item Accomodator examples: many-worlds, Bohmian mechanics, etc.
    \end{itemize}
    
\end{enumerate}

\end{frame}

\begin{frame}
\frametitle{Importance of Philosophy}
\begin{itemize}
    \item Usually, a boring, over-explaining vulture
    \item Here, a \alert{scout}
    \item Capacities of quantum channels, error probabilities of quantum algorithms
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Aha! Connection}
Who can I put in coherent superposition for 500 million years?
\begin{itemize}
    \item<1-> A human? 
    \item<2-> A computer!
\end{itemize}
\end{frame}
\end{document}
